
\documentclass[11pt,twocolumn,a4paper,DIV=calc]{scrartcl}
\usepackage[protrusion=true,expansion=true]{microtype}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{times}
\usepackage{helvet}


\begin{document}
%TBD: infos
\title{The title of the paper}
\author{anonymous authors}
\date{}
\maketitle


\section{Hints from etherpad}
	\subsection{Reading}

	\begin{itemize}
		\item read your paper multiple times
	   \item find out when and where it has been published
	   \item understand the relevant basics of the field
	   \item search for other papers on the same topic to judge the relevance and contribution of your paper
	     \item published at an earlier time or at a later time
	     \item dealing with other problems in the same field
	     \item dealing with similar problems in different fields
	     \item tackling a similar challenge or other challenges
	\end{itemize}

\subsection{Writing}

\begin{itemize}
	\item Write up a summary with your findings
   \item length restriction: fit it into 4 pages A4 max!
   \item two-column 11pt Times!
   \item please use LaTeX for the layout (see template below)

   \item You may (re-)use figures or formulas whenever appropriate (if referenced correctly)
   \item Do not re-use text from the paper (no copy\&paste)!

   \item upload your summary by the deadline to the skiconf tool
     \item authors remain anonymous => do NOT include your names!
     \item bonus: ensure that the PDF metadata does not disclose your login name etc.
   \item language: English
\end{itemize}

\subsection{General hints for summary}

\begin{itemize}
\item Briefly outline the "field" this paper belongs to, the challenges that exist in this field and how your paper fits into the bigger picture
 \item Explain the relevant basics and fundamentals
   \item What stuff do you have to know in order to understand the content of the paper and to judge its impact?
 \item Your summary should contain answers to the following:
   \item What are the problems to be solved? Why are they worthwhile to solve?
   \item What methods are used? How is the problem tackled?
   \item What results are obtained? What do the results mean?
 \item Additionally: outline the impact of the paper
   \item What is the "delta" that the authors of the paper achieved in comparison of the state of the art at the time the paper was published
   \item How is it different/better compared to related works?
     \item How has the paper been received by the scientific community?
     \item How do papers that have been published later talk about this paper?
     \item Is the delta of the paper of relevance today?
     \item Did the paper influence its field?
\end{itemize}

\subsection{General advice}
\begin{itemize}
 \item be as descriptive and concrete as necessary, but still as concise as possible
 \item give examples if suitable

 \item most important challenge
   \item your Summary should be *understandable on its own*
     \item you will have to leave out lots of (less relevant) details
     \item but: you may have to add things that are not described in the paper

  \item ask yourself: does the summary contain the most relevant contributions of the paper?

 \item do not confuse your summary with the "Abstract" at the beginning of a paper
   \item your summary contains more details than the abstract of the paper
   \item your summary contains information *about* the paper (which was not available when the paper was published)

  \item remember: do not copy text word by word from your paper (plagiarism)!!!

\end{itemize}

\newpage

\section{Introduction}

% Thematische Einordnung: Ziele des Ganzen, Onion Routing, anonymisierte Kommunikation (grob!)

\input{introduction.tex}

\section{Onion Routing/Technical background}

% Wie funktioniert das (theoretischer Überblick), 
% Paper aus Tor-Paper (41 Anonymous connections and onion routing, 48 Onion routing access configuration, 49 Towards an analysis of onion routing security, 27 Hiding routing information) 
% Einordnung in die Vorarbeiten (Bereits implementierte Anwendungen)

\input{onion_routing.tex}

\section{Tor}

% Inhalte des Papers (grob), Schwerpunkte (Verbesserungen in Tor gegenüber damals existierenden Systemen), Neuerungen in Tor, etc.
\input{tor.tex}

\section{Importance/Impact}

% Heutige Verwendung, Größe des Netzwerks, auch Contra-Argumente: Nutzung durch Kriminelle etc., Referenzierungen des Papers

\input{impact.tex}

\end{document}


